Carbonate chemistry at Ny-Ålesund

### 2022-08-12 awipev-CO2.Rmd
stratification

The relationship between the measured (Contros) and calculated pCO2
(blue line) is relatively poor. It is far from the 1:1 relationship
(black dashed line). The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.

@@

pHspec_pHseafet <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHseafet.png", plot = pHspec_pHseafet, width = 25, height = 25, units = "cm")
```
The relationship between spectrophotometric pH and SeaFET pH) and 
(blue line) is relatively good The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.

@@

## Stratification
```{r, echo=FALSE, message= FALSE, warning=FALSE}
# # we look at the distribution of data
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))

@@

sal_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=sal_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Salinity", limits = c(-1.1, 0.8), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.65, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']") +
#  annotate("text", x = 2, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
#  annotate("text", x = 2, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(sal_delta_plt)

# we look at temperature all depths
tmp <- d_all %>% 
  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = temp_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$temp_insitu_ctd ~ tmp$depth_group * tmp$montht))
# we look at temperature 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
                                      depth_group == '>8' ~ '8-12'))) %>% 
  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
  dplyr::group_by(depth_group2, montht)
tmp_delta <- tmp %>% 
  group_by(depth_group2, montht) %>% 
  dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>% 
  tidyr::pivot_wider(names_from = depth_group2, values_from = temp_med) %>% 
  dplyr::rename(median0_4m = "0-4",
                median8_12m = "8-12") %>% 
  dplyr::mutate(temp_delta = median0_4m - median8_12m)
kable(tmp_delta, digits = 2, caption = "Median temperature with (median0_4m - median8_12m)")
p <- tmp %>% 
  tidyr::drop_na() %>% 
  ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
temp_delta_plt <- tmp_delta %>% 
  #tidyr::drop_na() %>% 
  ggplot(aes(x = montht, y = temp_delta)) +
  #scale_x_discrete(expand = c(0, 0)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Temperature", limits = c(-2.1, 0.5), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "S['surface'] <  S['deep']") +
  # annotate("text", x = 2, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
  # annotate("text", x = 2, y = -1.8, label = substitute("T"["surface"] ~ "< T"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(temp_delta_plt)
# we look at density at all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>% 
  group_by(depth_group, montht)
p <- tidyr::drop_na(tmp) %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$density ~ tmp$depth_group * tmp$montht))

@@

den_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=den_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Density", limits = c(-1.5, 0.5), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "S['surface'] <  S['deep']") +
  # annotate("text", x = 2, y = 0.25, label = substitute("D"["surface"] ~ "> D"["deep"])) +
  # annotate("text", x = 2, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(den_delta_plt)
# we look at pHint_tot_sf at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x = as.factor(depth_group), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf vs depth", x = "Depth (m)", y= "pH (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))

# we look at pHint_tot_sf 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
                                                   depth_group == '>8' ~ '8-12'))) %>% 
  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
  dplyr::group_by(depth_group2, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group2 * tmp$montht))

@@

pHinsi_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
  scale_x_discrete("Month") +
  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "S['surface'] <  S['deep']") +
  # annotate("text", x = 1.5, y = 0.02, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
  # annotate("text", x = 1.5, y = -0.06, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(pHinsi_delta_plt)
# we look at pHint_tot_sf normalized at 4°C at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

@@

pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
  scale_x_discrete("Month", expand = c(0, 0)) +
  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.1), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "S['surface'] <  S['deep']") +
  # annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
  # annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

>>>>

The relationship between the measured (Contros) and calculated pCO2
(blue line) is relatively poor. It is far from the 1:1 relationship
(black dashed line). The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`  (`r N = reg$fit$n`)`.

@@

pHspec_pHseafet <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHseafet.png", plot = pHspec_pHseafet, width = 25, height = 25, units = "cm")
```
The relationship between spectrophotometric pH and SeaFET pH) and 
(blue line) is relatively good The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`  (`r N = reg$fit$n`)`.

@@

## Stratification
```{r, echo=FALSE, message= FALSE, warning=FALSE}
# we look at the distribution of data
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))

@@

sal_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=sal_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Salinity", limits = c(-1.1, 0.8), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.65, parse = TRUE, label = "S['surface'] > S['deep']") +
  annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(sal_delta_plt)

# we look at temperature all depths
tmp <- d_all %>% 
  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = temp_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$temp_insitu_ctd ~ tmp$depth_group * tmp$montht))
# we look at temperature 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
                                      depth_group == '>8' ~ '8-12'))) %>% 
  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
  dplyr::group_by(depth_group2, montht)
tmp_delta <- tmp %>% 
  group_by(depth_group2, montht) %>% 
  dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>% 
  tidyr::pivot_wider(names_from = depth_group2, values_from = temp_med) %>% 
  dplyr::rename(median0_4m = "0-4",
                median8_12m = "8-12") %>% 
  dplyr::mutate(temp_delta = median0_4m - median8_12m)
kable(tmp_delta, digits = 2, caption = "Median temperature with (median0_4m - median8_12m)")
p <- tmp %>% 
  tidyr::drop_na() %>% 
  ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
temp_delta_plt <- tmp_delta %>% 
  #tidyr::drop_na() %>% 
  ggplot(aes(x = montht, y = temp_delta)) +
  #scale_x_discrete(expand = c(0, 0)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Temperature", limits = c(-2.1, 0.5), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "T['surface'] > T['deep']") +
  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "T['surface'] <  T['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(temp_delta_plt)
# we look at density at all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>% 
  group_by(depth_group, montht)
p <- tidyr::drop_na(tmp) %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$density ~ tmp$depth_group * tmp$montht))

@@

den_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=den_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous("Density", limits = c(-1.5, 0.5), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "D['surface'] > D['deep']") +
  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "D['surface'] <  D['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(den_delta_plt)
# we look at pHint_tot_sf at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x = as.factor(depth_group), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf vs depth", x = "Depth (m)", y= "pH (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))

# we look at pHint_tot_sf 0 to 4 m vs more than 8 m
tmp <- d_all %>%
  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
  dplyr::mutate(depth_group2 = as.factor(
    case_when(
      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
      depth_group == '>8' ~ '8-12'
    )
  )) %>%
  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
  dplyr::group_by(depth_group2, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group2 * tmp$montht))

@@

pHinsi_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "pH['surface'] > pH['deep']") +
  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "pH['surface'] <  pH['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(pHinsi_delta_plt)
# we look at pHint_tot_sf normalized at 4°C at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

@@

pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  scale_x_discrete("Month", expand = c(0, 0)) +
  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
